---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# who-data


[![Build Status](https://travis-ci.org/ATFutures/who.svg)](https://travis-ci.org/ATFutures/who) 
[![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)

Data for [`who` repo](https://github.com/ATFutures/who).

### Installation

```{r, eval=FALSE}
devtools::install_github("ATFutures/who")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

`makefile` based. Files for [`worldpop`](http://www.worldpop.org.uk) must be
manually downloaded - see specific `[city]/worldpop` directories for details.
These are national level `zip`-archived files which need to be cropped to the
city level only, and are converted to `geotif` format. This can be done, and all
OSM data also downloaded into corresponding directories with a single `make`
call. Alternatively, the components can be executed with
```
make osm
make worldpop
```
Note that `make osm` will always overwrite any existing OSM data, whereas `make
worlpop` will only convert files if they've not already been converted.
